\bf The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-08-10 paper/paper.Rmd
Reknit entire paper from scratch

```{r appendix1-code, eval=FALSE}
library(tidyverse)
library(lubridate)
library(here)
library(sf)
library(viridis)
library(forestecology)
library(blockCV)
library(tictoc)

>>>>

```{r appendix1-code}
library(tidyverse)
library(lubridate)
library(here)
library(sf)
library(viridis)
library(forestecology)
library(blockCV)
library(tictoc)

### 2021-08-10 paper/paper.tex
Reknit entire paper from scratch

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{census_}\DecValTok{2013}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"scbi.stem2.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \CommentTok{# Convert date from character to date}
    \DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date),}
    \CommentTok{# Convert dbh to be in cm}
    \DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh)}\OperatorTok{/}\DecValTok{10}
\NormalTok{  ) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{census_}\DecValTok{2018}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"scbi.stem3.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date),}
    \DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh)}\OperatorTok{/}\DecValTok{10}
\NormalTok{  ) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Install development version of allodb using:}
\CommentTok{# remotes::install_github("forestgeo/allodb")}
\KeywordTok{library}\NormalTok{(allodb)}
\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \CommentTok{# Compute basal area:}
    \DataTypeTok{basal_area =} \FloatTok{0.0001} \OperatorTok{*}\StringTok{ }\NormalTok{pi }\OperatorTok{*}\StringTok{ }\NormalTok{(dbh1 }\OperatorTok{/}\StringTok{ }\DecValTok{2}\NormalTok{)}\OperatorTok{^}\DecValTok{2}\NormalTok{,}
    \CommentTok{# Compute above ground biomass:}
    \DataTypeTok{agb =} \KeywordTok{get_biomass}\NormalTok{(}
      \DataTypeTok{dbh =}\NormalTok{ dbh1,}
      \DataTypeTok{genus =}\NormalTok{ genus,}
      \DataTypeTok{species =}\NormalTok{ species,}
      \DataTypeTok{coords =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{78.2}\NormalTok{, }\FloatTok{38.9}\NormalTok{)}
\NormalTok{    )}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# }\AlertTok{TODO}\CommentTok{:}
\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{comp_x_var =}\NormalTok{ basal_area)}

\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{create_focal_vs_comp}\NormalTok{(comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(focal_ID, focal_sp, geometry, growth, comp)}
\CommentTok{## # A tibble: 6,296 x 5}
\CommentTok{##   focal_ID focal_sp   geometry growth comp             }
\CommentTok{##      <dbl> <fct>       <POINT>  <dbl> <list>           }
\CommentTok{## 1        4 nysy     (14.2 428)  0.103 <tibble [20 x 4]>}
\CommentTok{## 2        5 havi      (9.4 436)  0.150 <tibble [32 x 4]>}
\CommentTok{## 3       79 tiam       (40 381) -0.161 <tibble [20 x 4]>}
\CommentTok{## 4       80 caca     (38.7 422)  0.253 <tibble [12 x 4]>}
\CommentTok{## 5       96 libe       (60 310)  0.262 <tibble [14 x 4]>}
\CommentTok{## # ... with 6,291 more rows}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{growth_scbi <-}\StringTok{ }\KeywordTok{compute_growth}\NormalTok{(}\DataTypeTok{census_1 =}\NormalTok{ census_}\DecValTok{2013}\NormalTok{_scbi, }\DataTypeTok{census_2 =}\NormalTok{ census_}\DecValTok{2018}\NormalTok{_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{str_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)), }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}

@@

\CommentTok{# Compute focal versus competitor tree information}
\CommentTok{# ---------------------}
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{create_focal_vs_comp}\NormalTok{(comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}

@@

    \CommentTok{# Status update}
    \KeywordTok{str_c}\NormalTok{(}\StringTok{"Shuffle with permutation "}\NormalTok{, j, }\StringTok{" at "}\NormalTok{, }\KeywordTok{Sys.time}\NormalTok{()) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{print}\NormalTok{()}
\NormalTok{\}}

@@

@@

\NormalTok{growth_scbi <-}\StringTok{ }\KeywordTok{compute_growth}\NormalTok{(}\DataTypeTok{census_1 =}\NormalTok{ census_}\DecValTok{2013}\NormalTok{_scbi, }\DataTypeTok{census_2 =}\NormalTok{ census_}\DecValTok{2018}\NormalTok{_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{str_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)), }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\CommentTok{# make all species the same, needs to be factor with at least two}
\StringTok{    }\CommentTok{# levels}
\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{sp =} \KeywordTok{factor}\NormalTok{(}\StringTok{"A"}\NormalTok{, }\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"A"}\NormalTok{, }\StringTok{"B"}\NormalTok{)))}

@@

\NormalTok{    focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{create_focal_vs_comp}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi,}
            \DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi)}

@@

@@

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{census_}\DecValTok{2013}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"scbi.stem2.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \CommentTok{# Convert date from character to date}
    \DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date),}
    \CommentTok{# Convert dbh to be in cm}
    \DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh) }\OperatorTok{/}\StringTok{ }\DecValTok{10}
\NormalTok{  ) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{census_}\DecValTok{2018}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"scbi.stem3.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date),}
    \DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh) }\OperatorTok{/}\StringTok{ }\DecValTok{10}
\NormalTok{  ) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Install development version of allodb using:}
\CommentTok{# remotes::install_github("forestgeo/allodb")}
\KeywordTok{library}\NormalTok{(allodb)}
\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \CommentTok{# Compute basal area:}
    \DataTypeTok{basal_area =} \FloatTok{0.0001} \OperatorTok{*}\StringTok{ }\NormalTok{pi }\OperatorTok{*}\StringTok{ }\NormalTok{(dbh1 }\OperatorTok{/}\StringTok{ }\DecValTok{2}\NormalTok{)}\OperatorTok{^}\DecValTok{2}\NormalTok{,}
    \CommentTok{# Compute above ground biomass:}
    \DataTypeTok{agb =} \KeywordTok{get_biomass}\NormalTok{(}
      \DataTypeTok{dbh =}\NormalTok{ dbh1,}
      \DataTypeTok{genus =}\NormalTok{ genus,}
      \DataTypeTok{species =}\NormalTok{ species,}
      \DataTypeTok{coords =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{78.2}\NormalTok{, }\FloatTok{38.9}\NormalTok{)}
\NormalTok{    )}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{create_focal_vs_comp}\NormalTok{(comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{,}
        \DataTypeTok{comp_x_var =} \StringTok{"basal_area"}\NormalTok{)}
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(focal_ID, focal_sp, geometry, growth, comp)}
\CommentTok{## # A tibble: 6,296 x 5}
\CommentTok{##   focal_ID focal_sp   geometry growth comp             }
\CommentTok{##      <dbl> <fct>       <POINT>  <dbl> <list>           }
\CommentTok{## 1        4 nysy     (14.2 428)  0.103 <tibble [20 x 4]>}
\CommentTok{## 2        5 havi      (9.4 436)  0.150 <tibble [32 x 4]>}
\CommentTok{## 3       79 tiam       (40 381) -0.161 <tibble [20 x 4]>}
\CommentTok{## 4       80 caca     (38.7 422)  0.253 <tibble [12 x 4]>}
\CommentTok{## 5       96 libe       (60 310)  0.262 <tibble [14 x 4]>}
\CommentTok{## # ... with 6,291 more rows}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Simple feature collection with 1 feature and 17 fields
## Geometry type: POINT
## Dimension:     XY
## Bounding box:  xmin: 250 ymin: 582 xmax: 250 ymax: 582
## CRS:           NA
## # A tibble: 1 x 18
##   stemID sp     dbh1 codes1 status  dbh2 codes2 growth
## *  <dbl> <fct> <dbl> <chr>  <chr>  <dbl> <chr>   <dbl>
## 1  18823 quve   68.8 NULL   A       69.9 NULL    0.215
## # ... with 10 more variables: geometry <POINT>, family <chr>,
## #   genus <chr>, species <chr>, canopy_position <chr>,
## #   drought_tolerance <chr>, basal_area <dbl>, agb <dbl>, buffer <lgl>,
## #   foldID <fct>
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{Figures/internal-1} \end{center}

@@

\NormalTok{growth_scbi <-}\StringTok{ }\KeywordTok{compute_growth}\NormalTok{(}\DataTypeTok{census_1 =}\NormalTok{ census_}\DecValTok{2013}\NormalTok{_scbi, }\DataTypeTok{census_2 =}\NormalTok{ census_}\DecValTok{2018}\NormalTok{_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{str_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)), }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\CommentTok{# Compute basal area:}
\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{basal_area =} \FloatTok{1e-04} \OperatorTok{*}\StringTok{ }\NormalTok{pi }\OperatorTok{*}\StringTok{ }\NormalTok{(dbh1}\OperatorTok{/}\DecValTok{2}\NormalTok{)}\OperatorTok{^}\DecValTok{2}\NormalTok{)}

@@

\CommentTok{# Compute focal versus competitor tree information}
\CommentTok{# ---------------------}
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{create_focal_vs_comp}\NormalTok{(comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{,}
        \DataTypeTok{comp_x_var =} \StringTok{"basal_area"}\NormalTok{)}

@@

    \CommentTok{# Status update}
    \KeywordTok{str_c}\NormalTok{(}\StringTok{"Shuffle with permutation "}\NormalTok{, j, }\StringTok{" at "}\NormalTok{, }\KeywordTok{Sys.time}\NormalTok{()) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{print}\NormalTok{()}
\NormalTok{\}}
\CommentTok{## [1] "Shuffle with permutation 1 at 2021-08-09 18:21:51"}
\CommentTok{## [1] "Shuffle with permutation 2 at 2021-08-09 18:26:48"}
\CommentTok{## [1] "Shuffle with permutation 3 at 2021-08-09 18:31:46"}
\CommentTok{## [1] "Shuffle with permutation 4 at 2021-08-09 18:36:41"}
\CommentTok{## [1] "Shuffle with permutation 5 at 2021-08-09 18:41:31"}
\CommentTok{## [1] "Shuffle with permutation 6 at 2021-08-09 18:46:03"}
\CommentTok{## [1] "Shuffle with permutation 7 at 2021-08-09 18:50:32"}
\CommentTok{## [1] "Shuffle with permutation 8 at 2021-08-09 18:55:09"}
\CommentTok{## [1] "Shuffle with permutation 9 at 2021-08-09 18:59:38"}
\CommentTok{## [1] "Shuffle with permutation 10 at 2021-08-09 19:04:06"}
\CommentTok{## [1] "Shuffle with permutation 11 at 2021-08-09 19:08:36"}
\CommentTok{## [1] "Shuffle with permutation 12 at 2021-08-09 19:13:01"}
\CommentTok{## [1] "Shuffle with permutation 13 at 2021-08-09 19:17:25"}
\CommentTok{## [1] "Shuffle with permutation 14 at 2021-08-09 19:21:47"}
\CommentTok{## [1] "Shuffle with permutation 15 at 2021-08-09 19:26:20"}
\CommentTok{## [1] "Shuffle with permutation 16 at 2021-08-09 19:30:42"}
\CommentTok{## [1] "Shuffle with permutation 17 at 2021-08-09 19:35:05"}
\CommentTok{## [1] "Shuffle with permutation 18 at 2021-08-09 19:39:28"}
\CommentTok{## [1] "Shuffle with permutation 19 at 2021-08-09 19:43:51"}
\CommentTok{## [1] "Shuffle with permutation 20 at 2021-08-09 19:48:14"}
\CommentTok{## [1] "Shuffle with permutation 21 at 2021-08-09 19:52:37"}
\CommentTok{## [1] "Shuffle with permutation 22 at 2021-08-09 19:57:01"}
\CommentTok{## [1] "Shuffle with permutation 23 at 2021-08-09 20:01:29"}
\CommentTok{## [1] "Shuffle with permutation 24 at 2021-08-09 20:06:09"}
\CommentTok{## [1] "Shuffle with permutation 25 at 2021-08-09 20:10:42"}
\CommentTok{## [1] "Shuffle with permutation 26 at 2021-08-09 20:15:06"}
\CommentTok{## [1] "Shuffle with permutation 27 at 2021-08-09 20:19:29"}
\CommentTok{## [1] "Shuffle with permutation 28 at 2021-08-09 20:23:52"}
\CommentTok{## [1] "Shuffle with permutation 29 at 2021-08-09 20:28:15"}
\CommentTok{## [1] "Shuffle with permutation 30 at 2021-08-09 20:32:37"}
\CommentTok{## [1] "Shuffle with permutation 31 at 2021-08-09 20:36:59"}
\CommentTok{## [1] "Shuffle with permutation 32 at 2021-08-09 20:41:21"}
\CommentTok{## [1] "Shuffle with permutation 33 at 2021-08-09 20:45:43"}
\CommentTok{## [1] "Shuffle with permutation 34 at 2021-08-09 20:50:06"}
\CommentTok{## [1] "Shuffle with permutation 35 at 2021-08-09 20:54:29"}
\CommentTok{## [1] "Shuffle with permutation 36 at 2021-08-09 20:58:51"}
\CommentTok{## [1] "Shuffle with permutation 37 at 2021-08-09 21:03:16"}
\CommentTok{## [1] "Shuffle with permutation 38 at 2021-08-09 21:07:38"}
\CommentTok{## [1] "Shuffle with permutation 39 at 2021-08-09 21:12:01"}
\CommentTok{## [1] "Shuffle with permutation 40 at 2021-08-09 21:16:24"}
\CommentTok{## [1] "Shuffle with permutation 41 at 2021-08-09 21:20:47"}
\CommentTok{## [1] "Shuffle with permutation 42 at 2021-08-09 21:25:11"}
\CommentTok{## [1] "Shuffle with permutation 43 at 2021-08-09 21:29:34"}
\CommentTok{## [1] "Shuffle with permutation 44 at 2021-08-09 21:33:57"}
\CommentTok{## [1] "Shuffle with permutation 45 at 2021-08-09 21:38:20"}
\CommentTok{## [1] "Shuffle with permutation 46 at 2021-08-09 21:42:42"}
\CommentTok{## [1] "Shuffle with permutation 47 at 2021-08-09 21:47:05"}
\CommentTok{## [1] "Shuffle with permutation 48 at 2021-08-09 21:51:27"}
\CommentTok{## [1] "Shuffle with permutation 49 at 2021-08-09 21:56:05"}

@@

\begin{center}\includegraphics[width=1\linewidth]{Figures/appendix1-code-1} \end{center}

@@

\NormalTok{growth_scbi <-}\StringTok{ }\KeywordTok{compute_growth}\NormalTok{(}\DataTypeTok{census_1 =}\NormalTok{ census_}\DecValTok{2013}\NormalTok{_scbi, }\DataTypeTok{census_2 =}\NormalTok{ census_}\DecValTok{2018}\NormalTok{_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{str_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)), }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\CommentTok{# make all species the same, needs to be factor with at least two}
\StringTok{    }\CommentTok{# levels}
\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{sp =} \KeywordTok{factor}\NormalTok{(}\StringTok{"A"}\NormalTok{, }\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"A"}\NormalTok{, }\StringTok{"B"}\NormalTok{))) }\OperatorTok{%>%}
\StringTok{    }\CommentTok{# Compute basal area:}
\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{basal_area =} \FloatTok{1e-04} \OperatorTok{*}\StringTok{ }\NormalTok{pi }\OperatorTok{*}\StringTok{ }\NormalTok{(dbh1}\OperatorTok{/}\DecValTok{2}\NormalTok{)}\OperatorTok{^}\DecValTok{2}\NormalTok{)}

@@

\NormalTok{    focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{create_focal_vs_comp}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi,}
            \DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{, }\DataTypeTok{comp_x_var =} \StringTok{"basal_area"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi)}

@@

\begin{center}\includegraphics[width=1\linewidth]{Figures/appendix2-code-1} \end{center}

@@

\hypertarget{compare-pred-var}{%
\section{Appendix 3: Compare predictor
variables}\label{compare-pred-var}}

In the above code we use the basal area of an individual as a continuous
predictor variable. But the package allows the user to specify any
predictor variable in the \texttt{comp\_x\_var} argument of
\texttt{create\_focal\_vs\_comp} function. Here we use the
cross-validated model comparison to see which of two possible predictor
variables, basal area or above ground biomass, best explains growth.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{census_}\DecValTok{2013}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"scbi.stem2.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date), }\DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh)}\OperatorTok{/}\DecValTok{10}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{census_}\DecValTok{2018}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"scbi.stem3.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date), }\DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh)}\OperatorTok{/}\DecValTok{10}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{growth_scbi <-}\StringTok{ }\KeywordTok{compute_growth}\NormalTok{(}\DataTypeTok{census_1 =}\NormalTok{ census_}\DecValTok{2013}\NormalTok{_scbi, }\DataTypeTok{census_2 =}\NormalTok{ census_}\DecValTok{2018}\NormalTok{_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{str_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)), }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{left_join}\NormalTok{(sp_info, }\DataTypeTok{by =} \StringTok{"sp"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{sp =} \KeywordTok{as.factor}\NormalTok{(sp), }\DataTypeTok{basal_area =} \FloatTok{1e-04} \OperatorTok{*}\StringTok{ }\NormalTok{pi }\OperatorTok{*}\StringTok{ }\NormalTok{(dbh1}\OperatorTok{/}\DecValTok{2}\NormalTok{)}\OperatorTok{^}\DecValTok{2}\NormalTok{, }\DataTypeTok{agb =} \KeywordTok{get_biomass}\NormalTok{(}\DataTypeTok{dbh =}\NormalTok{ dbh1,}
        \DataTypeTok{genus =}\NormalTok{ genus, }\DataTypeTok{species =}\NormalTok{ species, }\DataTypeTok{coords =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{78.2}\NormalTok{, }\FloatTok{38.9}\NormalTok{)))}

\NormalTok{n_fold <-}\StringTok{ }\DecValTok{4}
\NormalTok{fold1 <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{0}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold2 <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{150}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold3 <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{0}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{fold4 <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{150}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{comp_dist <-}\StringTok{ }\FloatTok{7.5}

\NormalTok{focal_vs_comp_ba <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{create_focal_vs_comp}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{,}
        \DataTypeTok{comp_x_var =} \StringTok{"basal_area"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi)}

\NormalTok{focal_vs_comp_agb <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{create_focal_vs_comp}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{,}
        \DataTypeTok{comp_x_var =} \StringTok{"agb"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi)}

\NormalTok{focal_vs_comp_ba }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{pull}\NormalTok{(.estimate)}
\CommentTok{## [1] 0.14}

\NormalTok{focal_vs_comp_agb }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{pull}\NormalTok{(.estimate)}
\CommentTok{## [1] 2.08}
\end{Highlighting}
\end{Shaded}

Here we see that basal area does a much better job than above ground
biomass.

\hypertarget{compare-group-var}{%
\section{Appendix 4: Compare grouping
variables}\label{compare-group-var}}

The package also allows the user to specify the categorical predictor
grouping variable. Here we compare two different such variables: species
and the potential canopy position of that species. If we had
individual-level crown classes (\citet{smith_practice_1986} dominant,
codominant, intermediate and suppressed) that could also be used.
